Full Title

### 2018-01-24 cones/paper/cones.tex
Finished universality material.
Got it into a state where I only need to prove the full abstraction things.

\begin{definition}
  Let $\sigma$ be a strategy for a game $A$.  
  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of complete strategies; i.e., there exist $\sigma_\alpha$ such that $T_\sigma=\bigcup T_{\sigma_\alpha}$ and $D_\sigma=\bigcup D_{\sigma_\alpha}$.
\end{definition}

@@

We define a game $\oc A$ as follows.  
The arena for $\oc A$ is the same as the arena for $A$, but the set of plays is given by
\[
  P_{\oc A} = \{s\in L_A\suchthat s\vert_m\in P_A\text{ for each initial move $m$}\}\,.
  \]
There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\coh\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.  
See \cite{SamsonGuyIAPassive} for full details.

@@

\begin{proposition}
  Let $\G_{D,vis,rec}$ be the category of games and \emph{recursive} visible strategies.  
  Then every morphism in $\G$ is definable in Idealized Algol.
\end{proposition}
\begin{proof}
  This follows from the corresponding results for PCF, together with the \emph{innocent factorization} result of \cite{SamsonGuyIAPassive}.  
  See also 
\end{proof}

@@

Our definability results will hinge on a \emph{factorization theorem}, showing that every nondeterministic strategy may be written as the composition of a deterministic strategy with the nondeterministic `oracle' $\top$.

\section{Cones on Monoidal Functors}

\subsection{Surjective and winning strategies}

A useful fact about the category $\G$ of games and deterministic strategies, proved in \cite{hylandSchalkGames}, is that it admits a faithful, monoidal and linearly distributive functor into the category $\Rel$ of sets and relations, with monoidal structure given by the Cartesian product and exponentials given by the multiset comonad $W$.  
The functor sends a game $A$ to the set $P_A$ and sends a strategy $\sigma\from A\implies B$ to the relation
\[
  \grel{\sigma}=\{(s\vert_A,s\vert_B)\suchthat s\in\sigma\}\subset P_A\times P_B
  \]

Given a strategy $\sigma\from A\implies B$, we say that $\sigma$ is \emph{surjective} if $\grel{\sigma}$ is a surjective relation; i.e., if for any $b\in P_B$ there exists some $s\in\sigma$ such that $s\vert_B=b$.  
Monoidality and linear distributivity of the Hyland-Schalk functor $\G\to\Rel$ show that the composition of surjective strategies is surjective, as is the tensor product of surjective strategies and the bang of a surjective strategy.

Given a strategy $\sigma\from A\implies B$, we say that $\sigma$ is \emph{winning} if $\sigma$ is total and if for all positions $s\in\sigma$, if $sb\in\sigma$, where $b$ is an $O$-move in $B$, then there is some $t\in\sigma$ such that $sb\prefix t$ and $t$ ends with a move in $B$.

Once again, the composition, tensor product and bang of winning strategies is still winning.  
One way of seeing this is by relating our definition to the definition of a winning strategy given in \cite{abramskyjagadeesangames}, in which a game comes attached with a set of winning infinite positions.  
Then we say that a strategy $\sigma$ is winning if it is total and if every infinite position arising as the limit of plays in $\sigma$ is a winning position.  
If $A$ and $B$ are such that every infinite position is winning, then our notion of a winning strategy coincides with that notion.

The reason we are interested in surjective winning strategies is that they preserve top strategies:

\begin{lemma}
  We say that a game $A$ is \emph{$P$-winning} if for all $O$-positions $s\in P_A$ there exists some $a$ such that $sa\in P_A$.  
  Let $A,B$ be $P$-winning games, and let $\sigma\from A\implies B$ be a surjective winning strategy.  
  Write $\top_A$ for the (nondeterministic) strategy given by $T_{\top_A}=P_A$ and $D_{\top_A}=P_A^\omega$ (i.e., the only divergent plays are the infinite ones), and do the same for $B$.
  Then $\top_A;\sigma=\top_B$.  
\end{lemma}
\begin{proof}
  We can show that $T_{\top_A;\sigma}=T_{\top_B}$ from surjectivity of $\sigma$, using the Hyland-Schalk functor, since the equivalent result clearly holds in $\Rel$.  
  Now suppose that $s$ is some divergent position in $\top_A;\sigma$.  
  Then $s=\s\vert_B$, where $\s$ is a position in $\sigma$ and $\s\vert_A$ is a divergent position in $A$.
  Then $\s\vert_A$ must be infinite; since $\sigma$ is winning, this means that $\s\vert_B$ must be infinite as well, and therefore that $s\in D_{\top_B}$.  
  \label{lem:sw}
\end{proof}

We now define a category $\G_{sw}$ whose objects are $P$-winning games and where the morphisms from a game $A$ to a game $B$ are deterministic surjective winning strategies from $A$ to $B$.  
We write $\G_{sw,rec}$ for the category where the morphisms are \emph{recursive} surjective, winning strategies.

Write $j$ for the inclusion $\G_{sw,rec}\hookrightarrow\G_{rec}$, and write $J$ for the inclusion functor $\G\hookrightarrow\G_{ND}$ that sends a deterministic strategy $\sigma$ to the strategy given by $T=\sigma$ and $D=\pocl\{s\in\sigma^-\suchthat sa\not\in\sigma\forall a\}$
Then the lemma we have just proves means that
\[
  \top \from I \Rightarrow J\circ j
  \]
is a natural transformation, where $I$ is the constant $I$ functor.

Moreover, we would expect Lemma \ref{lem:sw} to hold in \emph{any} sensible game-semantics model of nondeterministic PCF, so the following makes sense as a definition

\begin{definition}
  A \emph{game semantics category for nondeterministic PCF} is a category $\D$ together with a functor $J\from \G_{rec}\to\D$ and a natural transformation $\top\from I\Rightarrow J\circ j\from\G_{sw,rec}\to\D$.  
\end{definition}

\subsection{Generalized monoidal natural transformations}

We will need one more technical definition.

Let $\C'$,$C'$,$\D'$,$\D$ be monoidal categories, let $f\from\C'\to\C$, $g\from \D'\to \D$ be oplax monoidal functors and let $F\from\D'\to\C'$, $G\from\D\to\C$ be lax monoidal functors, as in Figure \ref{fig:generalized-monoidal-setup}.

\begin{figure}
  \[
    \begin{tikzcd}[row sep=large, column sep=large]
      \D' \arrow[r, "F", ""'{name=F}] \arrow[d, "g"']
        & \C' \arrow[d, "f"] \\
      \D \arrow[r, "G"', ""{name=G}]
        & \C
      \arrow[Rightarrow, from=F, to=G, "\phi"]
    \end{tikzcd}
    \]
  \caption{A generalized monoidal natural transformation $\phi$ is a particular sort of natural transformation between composites of lax and oplax monoidal functors.}
  \label{fig:generalized-monoidal-setup}
\end{figure}

We say that a natural transformation $\phi\from fF\bigto Gg$ is a \emph{generalized monoidal natural transformation} if the following two diagrams commute for all objects $X,Y$ of $\D'$:
\begin{mathpar}
  \begin{tikzcd}
    f F X \tensor f F Y \arrow[r, "\phi_X \tensor \phi_Y"]
      & G g X \tensor G g Y \arrow[d, "m_G"] \\
    f (F X \tensor F Y) \arrow[u, "m_f"] \arrow[d, "f m_F"']
      & G (g X \tensor g Y) \\
    f F (X \tensor Y) \arrow[r, "\phi_{X \tensor Y}"]
      & G g (X \tensor Y) \arrow[u, "G m_g"']
  \end{tikzcd}
  \and
  \begin{tikzcd}[column sep=small, row sep=small]
    %
      & f F I_{\D'} \arrow[rr, "\phi_I"]
        &[-1.2em]
          &[-1.2em] G g I_{\D'} \arrow[dr, "G \epsilon_g"]
            & \\
    f I_{\C'} \arrow[ur, "f \epsilon_F"] \arrow[drr, "\epsilon_f"]
      &
        &
          &
            & G I_{\D} \\
    %
      &
        & I_{\C} \arrow[urr, "\epsilon_G"]
          &
            &
  \end{tikzcd}\,.
\end{mathpar}
The particular structure that generalized natural transformations fit into is that of a \emph{double category} (see \cite{LimitsInDoubleCategories} for the definition); in particular, the double category $\SymmMonCat$ introduced in \cite{AdjointsInDoubleCategories}, in which the objects are symmetric monoidal categories, the horizontal morphisms are lax symmetric monoidal functors, the vertical morphisms are oplax symmetric monoidal functors and the $2$-cells are generalized monoidal natural transformations as defined above.

Generalized monoidal natural transformations may thus be composed either horizontally or vertically in the usual way; i.e., given a pair of squares as in Figure \ref{fig:generalized-monoidal-setup} that may be pasted together along an edge, then we may define a generalized monoidal natural transformation across the pasted square.  
We write $\hc{\phi}{\psi}$ for the horizontal composition of natural transformations $\phi,\psi$ pasted together along an oplax monoidal functor and $\vc{\phi}{\psi}$ for the vertical composition of natural transformations $\phi,\psi$ pasted together along a lax monoidal natural functor.

\subsection{The cone of a monoidal functor}

Let $j\from \C'\to \C$ be an oplax monoidal functor.  
We define a \emph{$j$-category} to be a category $\D$ together with a lax monoidal functor $J\from\C\to\D$ and a generalized natural transformation $\phi\from I \to Jj$:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
      & I \arrow[d, "I"] \\
    \C \arrow[r, "J"', ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=J, "\phi"]
  \end{tikzcd}\,.
  \]
\begin{example}
  For example, our previous definition of a game semantics category for nondeterministic PCF can be thought of as a $j$-category, where $j$ is the inclusion functor $\G_{sw,rec}\hookrightarrow\G_{rec}$.  
\end{example}
We define a \emph{morphism of $j$-categories} going from a $j$-category $(\D',J',\phi')$ to a $j$-category $(\D,J,\phi)$ to be a lax monoidal functor $\F\from \D'\to\D$, sending $I$ to $I$, such that $J=\F\circ J'$ and $\phi$ is the vertical composition of $\phi'$ with the `identity transformation' given by this identity; i.e.:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
      & I \arrow[d, "I"] \\
    \C \arrow[r, "J'"'{name=Jprimedown}, ""{name=Jprime}] \arrow[d, "\id"']
      & \D' \arrow[d, "\F"] \\
    \C \arrow[r, "J", ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=Jprime, shift left=1.5ex, "\phi'"]
    \arrow[Rightarrow, from=Jprimedown, to=J, shift left=1.5ex, "\id"]
    \arrow[Rightarrow, from=term, to=J, shift right=3ex, "\phi"' near end]
  \end{tikzcd}\,.
  \]
Our main technical result in this section will be the following:
\begin{proposition}
  The category $j$-$\Cat$ of $j$-categories and $j$-category morphisms has an initial object $C_j$
\end{proposition}
By analogy with homotopy theory, we call this initial object the \emph{mapping cone} or \emph{cone} on $j$.

To see why this is useful, consider another important topic from the theory of semantics.  
We say that a $j$-category $(\D,J,\phi)$ satisfies \emph{$\phi$-factorization} if for any pair of objects $A$ and $B$ of $\C$ and for every morphism $f\from JA \to JB$ in $\D$, we may write $f$ as a composite
\[
  JA \xrightarrow{\lunit;\phi_X\tensor JA}
  Jj X \tensor JA \xrightarrow{m_J}
  J (jX \tensor A) \xrightarrow{J f'}
  JB\,,
  \]
where $X$ is some object of $\C'$ and $f'\from jX \tensor A\to B$ is some morphism in $\C$.
\begin{example}
  In the case that $j$ is the inclusion $\G_{sw,rec}\hookrightarrow\G_{rec}$, and $\phi=\top$, $\phi$-factorization is the same as \emph{deterministic factorization}: the idea that every morphism can be written as the composition of a deterministic recursive strategy with $\top_X$ for some $X$.
\end{example}

Then the following result is easy to prove:
\begin{proposition}
  Let $(\D,J,\phi)$ be a $j$-category satisfying $\phi$-factorization.  
  Suppose $\F\from\D'\to\D$ is a morphism of $j$-categories.  
  Then $\F$ is a full functor.
\end{proposition}
In particular, the unique $j$-category morphism $C_j\to\D$ is a full functor.  
This is useful, because we are viewing game semantic models of nondeterministic PCF as $j$-categories (for a particular $j$), and therefore we can see that $C_j$ admits a full functor into every such model that satisfies deterministic factorization.  
Since we typically require that our models satisfy such a factorization result, we can form any such model by taking $C_j$ and imposing some equivalence relation on the morphisms.  
This suggests that we might consider $C_j$ itself as our model of nondeterministic PCF.

\subsection{Constructing the cone}

We will now define what the cone $C_j$ is and give an outline of why it is initial in the category of $j$-categories.

Recall that we start with an oplax symmetric monoidal functor $j\from \C'\to\C$.  
The objects of $C_j$ are the objects of $\C$.  
Given objects $A,B$ of $\C$, the class of morphisms $A\to B$ is given by the colimit of the functor
\[
  \oppcat{\C'} \xrightarrow{\oppcat{j}}
  \oppcat{\C} \xrightarrow{\C[\blank\tensor A,B]}
  \Set\,.
  \]
That is, a morphism from $A$ to $B$ is a pair $(X,f)$, where $X$ is an object of $\C'$ and $f\from jX \tensor A \to B$ is a morphism in $\C$.  
Furthermore, $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute:
\[
  \begin{tikzcd}
    j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
      & B \\
    j X \tensor A \arrow[ur, "f"']
      &
  \end{tikzcd}\,.
  \]
Given morphisms $(X,f)\from A \to B$, $(Y,g)\from B \to C$, the composite is given by $(Y\tensor X,f;g)$, where $f;g$ is the following composite in $\C$:
\begin{align*}
  j(Y\tensor X)\tensor A & \xrightarrow{m_j\tensor A}
    (jY \tensor jX) \tensor A \\ & \xrightarrow{\assoc}
      jY \tensor (jX \tensor A) \\ & \xrightarrow{jY \tensor f}
        jY \tensor B \xrightarrow{g}
          C\,.
\end{align*}
We can prove that this composition is associative using the usual coherence theorems for monoidal categories.  
Similarly, the symmetric monoidal structure from $\C$ induces a symmetric monoidal structure on $C_j$.  
If $\C$ is symmetric monoidal \emph{closed}, then so is $C_j$.

There is a functor $J\from \C\to C_j$ that is the identity on objects and which sends a strategy $f\from A \to B$ to the strategy
\[
  j I \tensor A \xrightarrow{\epsilon_j\tensor A}
  I \tensor A \xrightarrow{\lunit\inv}
  A \xrightarrow{f} B\,.
  \]
This functor is (strong) symmetric monoidal with respect to the monoidal structure on $C_j$.  
Lastly, the natural transformation $\phi\from I \Rightarrow J\circ j$ is given by the composite
\[
  \phi_X = jX \tensor I \xrightarrow{\runit\inv}
  jX\,,
  \]
considered as a morphism from $I$ to $jX$ in $C_j$.  
Proving that this is indeed a natural transformation makes essential use of the equivalence relation on morphisms in $C_j$.  
We can also prove that $\phi$ is a generalized monoidal natural transformation.  
Therefore, $C_j$ is a $j$-category.

Now suppose that $(\D,F,\psi)$ is another $j$-category.  
We define a functor $H\from C_j\to\D$ that sends an object $A=JA$ in $C_j$ to the object $FA$ in $\D$.  
Moreover, we send a morphism $f\from jX\tensor A \to B$ from $JA$ to $JB$ in $C_j$ to the following composite in $\D$:
\begin{align*}
  FA \xrightarrow{\lunit;\psi_X\tensor FA}
  FjX \tensor FA \xrightarrow{m_F}
  F (jX \tensor A) \xrightarrow{F f}
  F B\,.
\end{align*}
Proving that this is indeed a functor is a little tricky, and relies on $\psi$ being a generalized monoidal natural transformation.  
We can then go through and check that $H$ is indeed a morphism of $j$-categories.

In order to prove uniqueness, note that, as a morphism of $j$-categories, $H$ is determined on morphisms of the form $Jf$ by the equation $F = H \circ J$ and on morphisms of the form $\phi_X$ by the equation $\psi=\vc{\phi}{H}$.  
But now, if $f\from jX\tensor A \to B$ is any morphism from $A$ to $B$ in $C_j$, we may write $f$ as the composite
\[
  JA \xrightarrow{\lunit;\phi_X\tensor A}
  JjX \tensor JA \xrightarrow{m_J}
  J (jX \tensor A) \xrightarrow{Jf}
  JB\,;
  \]
i.e., $C_j$ satisfies $\phi$-factorization.  
Since the functor $H$ is required to be monoidal, this implies that it is determined everywhere on $C_j$ by the requirement that it be a morphism of $j$-categories.
Therefore, $C_j$ is initial in the category of $j$-categories.

A consequence of the initiality of the cone construction is that it is \emph{functorial}; that is, given a square of the following form:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "F", ""'{name=term}] \arrow[d, "j"']
      & \D' \arrow[d, "j'"] \\
    \C \arrow[r, "G"', ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=J, "\psi"]
  \end{tikzcd}\,,
  \]
where horizontal arrows correspond to lax monoidal functors and vertical arrows to monoidal functors, we get an induced lax monoidal functor $C_{j}\to C_{j}$, in a way that respects horizontal pasting of squares.
In particular, if $\C$ and $\C'$ have linear structures, compatible with $j$, then $C_j$ inherits a linear structure.

\section{Denotational Semantics}

We now restrict our attention to the inclusion functor $j\from G_{sw,rec}\hookrightarrow \G_{rec}$.  
Then $C_j$ inherits a linear structure from $\G_{rec}$.

\subsection{Extensional order}

Let $\sigma,\tau\from I \to \bN$ be morphisms in $C_j$, corrseponding to morphisms $\sigma'\from jX \to \bN$, $\tau'\from jY \to \bN$ in $\G_{rec}$.  
We say that $\sigma\lst\tau$ if the following two conditions hold:
\begin{itemize}
  \item If there exists $s\in \sigma'$ such that $s\vert_{\bN}=qn$, then there exists $t\in\tau'$ such that $t\vert_{\bN}=qn$.
  \item If $\sigma'$ is winning then $\tau'$ is winning.
\end{itemize}
In general, given strategies $\sigma,\tau\from I \to A$ in $C_j$, we say that $\sigma\lst\tau$ if for all morphisms $\rho\from A \to \bN$ we have $\sigma;\rho\lst\tau;\rho$.

We can show that this is well-defined; i.e., that it respects the equivalence relation we have already defined on morphisms.  
This is a good exercise to show the importance of surjective and winning strategies to our model.

\subsection{Countable nondeterminism}

In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that morphisms are strategies for $\oc\bN\tensor A \to B$, rather than $X \tensor A \to B$ for an arbitrary game $X$.

Since $\oc\bN$ has the structure of a comonoid, it gives rise to an oplax monoidal functor
\[
  n\from I \to \G_{rec}\,,
  \]
where $I$ is the one-object monoidal category.  
Moreover, this functor is linear distributive from the trivial linear structure on $I$ on to $\G$.
The cone $C_n$ is therefore a linear category.

Since $\G_{sw,rec}$ is a sub-linear category of $\G_{rec}$, the functor $n$ factors through a functor $n'\from I \to \G_{rec}$.  
By initiality of the cone construction, this gives rise to a functor $C_n\to C_j$.  
Our model of nondeterministic PCF will be the category $\C$ that is the image of this functor.
A morphism in $\C$ from a game $A$ to a game $B$ will be a strategy for $\oc \bN \tensor A \to B$, but the equivalence relation on morphisms is that from $C_j$.  
For example, two morphisms $f,g\from \oc\bN\to A$ are equivalent in $\C$ if there is a surjective winning strategy $\oc\bN\to \oc\bN$ commuting with $f$ and $g$, but they are not equivalent in $C_n$.

In fact, once we have applied the extensional quotient, there is no difference between working in $\C$ and working in $C_n$.  
We will use $\C$, because it is closer to being a fully abstract model for nondeterministic PCF before we apply the extensional quotient.

\subsection{The denotation of a term}

Let $M=C[\wn]\from T$ be a term of nondeterministic PCF, where $C[-]$ is a PCF context (i.e., a context not mentioning the constant $\wn$).  
Then the denotation of $M$ in $\C$ is given by the following composite:
\[
  I \xrightarrow{\phi_{\oc\bN}}
  \oc \bN \xrightarrow{J (\deno{\lambda n. C[n]})}
  \deno{T}
  \]
In other words, when considered as a morphism in $\G_{rec}$, $\deno{M}$ is precisely the denotation of the term $\lambda n.C[n]$ in $\G_{rec}$.

\subsection{Relation to our previous model}

Since our Harmer-McCusker-style model $\G_{ND}$

>>>>

\begin{definition}
  Let $\sigma$ be a strategy for a game $A$.  
  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of countably many complete strategies; i.e., there exist $\sigma_n$ such that $T_\sigma=\bigcup T_{\sigma_n}$ and $D_\sigma=\bigcup D_{\sigma_n}$.
\end{definition}

@@

We define a game $\oc A$ as follows.  
The arena for $\oc A$ is the same as the arena for $A$, but the set of plays is given by
\[
  P_{\oc A} = \{s\in L_A\suchthat s\vert_m\in P_A\text{ for each initial move $m$}\}\,.
  \]
There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\coh\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.  
This construction is essentially the co-Kleisli category on a comonad given by $\oc$, but certain technical issues prevent us from presenting it in this way.
See \cite{SamsonGuyIAPassive} for full details.

@@

\begin{proposition}
  Let $\G_{D,vis,rec}$ be the category of games and \emph{recursive} visible strategies.  
  Then $\G_{D,vis,rec}$ is a fully abstract model of Idealized Algol in which every morphism is definable.
\end{proposition}
\begin{proof}
  This follows from the corresponding results for PCF, together with the \emph{innocent factorization} result of \cite{SamsonGuyIAPassive}.  
  See also \cite{MurawskiUniversality}.
\end{proof}

@@

Our definability results will hinge on a \emph{factorization theorem}, showing that every nondeterministic strategy may be written as the composition of a deterministic strategy with the nondeterministic `oracle' $\top_{\bN}$.  
We can then deduce definability from definability in the model of deterministic Idealized Algol.

Note that our result is a bit simpler than the corresponding result in \cite{mcCHFiniteND}; this is because it is easier to model a countable source of nondeterminism than a `finite but arbitrarily large' source.

\begin{proposition}
  Let $\sigma\from I \to A$ be a strategy for a game $A$ in $\G_{ND}$.
  Then we may write $\sigma$ as $\top_{\bN};\Det(\sigma)$, where $\Det(\sigma)\from \oc\bN\to A$ is a deterministic strategy and $\top_{\bN}$ is the strategy for $\oc\bN$ given by
  \begin{itemize}
    \item $T_{\top_{\bN}}=P_{\oc\bN}$.
    \item $D_{\top_{\bN}}$ is the set of infinite positions in $T_{\top_\bN}$.
  \end{itemize}
\end{proposition}

\begin{proof}
  We begin by fixing an injection $\code_A$ from the set of $P$-moves in $A$ into the natural numbers.  
  In the enumerated case, this is given to us already.

  We first assume that the strategy $\sigma$ is complete.
  Then the strategy $\Det(\sigma)$ is very easy to describe.  
  For each $O$-position $sa\in T_\sigma$, we have some set $B$ of possible replies to $sa$, which we order as $b_1,b_2,\cdots$, where $\code_A(b_1)<\code_A(b_2)<\cdots$.  
  We insert a request to the oracle for a natural number; then, depending on her answer $j$, we play the next move as follows:
  \begin{itemize}
    \item If $0 < j \le \code_A(b_1)$, then play $b_1$.
    \item If $\code_A(b_n) < j \le \code_A(b_{n+1})$ then play $b_{n+1}$.
    \item If $j = 0$ and $sa\in D_\sigma$, then play nothing, and put the resulting play inside $D_{\Det(\sigma)}$.  
      Otherwise, play $b_1$.
  \end{itemize}
  Lastly, we close under limits to make the strategy $\Det(\sigma)$ complete.  
  $\Det(\sigma)$ is clearly nondeterministic.  
  Checking that $\top_{\bN};\Det(\sigma)=\sigma$ is easy for finite plays; for infinite plays, it follows by completeness of $\sigma$.

  Lastly, if $\sigma$ is the union of complete strategies $\sigma_1,\sigma_2,\cdots$, we insert an additional request to the oracle immediately after the very first move by player $O$; after receiving a reply $k$, we play according to $\sigma_k$.
\end{proof}

Note that in the recursive case, $\Det(\sigma)$ is clearly recursively presentable if $\sigma$ is.  
Furthermore, if $\sigma$ is visible, then so is $\Det(\sigma)$.
